Codebook created on 2025-06-19 at 2025-06-19 10:42:57

### 2025-06-19 codebook_data.Rmd
manual translation error

---
title: "Codebook created on 2025-06-19 at 2025-06-19 09:49:51"
output: github_document
---

@@

## Dataset description
The data contains 633 cases and 29 variables.

>>>>

---
title: "Codebook created on 2025-06-19 at 2025-06-19 10:42:57"
output: github_document
---

@@

## Dataset description
The data contains 634 cases and 29 variables.
